ABX usage

### 2019-12-13 scripts/27_maASlin2.Rmd
update

```{r}
# get the MRN of my target samples 
link <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 11252019 wo Censor .xlsx',
                    sheet = 4) %>% 
  dplyr::select(pt_id, MRN)

@@

@@

>>>>

```{r}
# get the MRN of my target samples 
link <- read_excel('/Volumes/castoricenter/CAR-Tcell_and_Microbiota/CTC Event Table 12122019.xlsx',
                    sheet = 4) %>% 
  dplyr::select(pt_id, 
                MRN,
                )

@@

pheno %>% 
  write_csv('../data/cleaned_pheno/final_pheno.csv')
```

@@

```{r}
source('~/MSK/work/microbiome_db/SQL/scripts/get_data_from_query_OTU.R')
get_data_from_query_OTU(0,'antibiotics_ag') 
dbListTables(con) %>% data.frame() %>% filter(grepl("_ag",.)) 
```

### 2019-12-13 scripts/29_abx_usage.Rmd
update

@@

```{r}
# create a table that has Y and N for abx usage 4 weeks prior to the baseline sample collection date
fil <- abx %>% 
  filter(startday <= 0 ) %>% 
  distinct(MRN)

>>>>

```{r}
### Using the clinical data info from ctc.medications
ctc.medications.srx %>% 
  filter(MRN == '38009710' & drug_name == 'vancomycin') %>% 
  dplyr::select(MRN, drug_name, start_datetime, stop_datetime)

ctc.medications.srx %>% 
  filter(MRN == '35399272') %>% 
  dplyr::select(MRN, drug_name, start_datetime, stop_datetime) %>% 
  filter(str_detect(drug_name, 'cephalexin'))

@@

```{r}
# create a table that has Y and N for abx usage 4 weeks prior to the baseline sample collection date
# only keep the MRN that have Y for abx 4 weeks prior to the baseline sample collection date
fil <- abx %>% 
  filter(startday <= 0 ) %>% 
  distinct(MRN)
